\section{Misc. Literature Quotes}

In February 2014 on the Big Island, the utility reports that 10\% of its circuits hit unstable levels \cite{trabish_solar_2014}.

Photovoltaics affect power quality by introducing harmonics \cite{anurangi_effects_2017}. The power feed-in of PV generation in rural low-voltage grids can influence power quality (PQ) as well as facility operation and reliability \cite{rita_pinto_impact_2016}.

Models, not actual installations \cite{anurangi_effects_2017,bayindir_effects_2016,farhoodnea_power_2012,shafiullah_experimental_2014}. Or data taken for only one week \cite{kucuk_assessment_2013}.

``across all business sectors, the U.S. economy is losing between \$104 billion and \$164 billion a year to outages and another \$15 billion to \$24 billion to PQ phenomena'' \cite{elphick_summary_2015} India lost more than \$9.6 billion in 2008 due to power quality, and Europe lost \$150 billion per year \cite{laskar_power_2012}.

A study of the island of Porto Santo in Portugal found that intermittent nature of installed photovoltaic and wind energy could result in a potential drop in frequency of 12 Hz, lasting as long as 7 seconds \cite{delgado_solutions_2011}.

Reduced input voltage can cause excessive power supply heat dissipation, resulting in reduced mean time between failures (MTBF). In addition, rectifiers and DC-to-DC converter switching transistors draw high-peak currents, which raise their junction temperatures. These temperature excursions take a toll on semiconductor longevity. High input voltage can also puncture a power supply's rectifier and switching transistor junctions, causing MTBF reduction and eventual breakdown. High-voltage transients lasting microseconds can permanently wreck the power supply and its electronic equipment load. \cite{dedad_when_2008}.

Solar panels connected to low voltage networks will result in over-voltages, the switching frequency of the converters in wind turbines causes high-frequency signals flowing into the grid, and harmonics are generated by EV chargers. \cite{zavoda_power_2018}

OPQ Boxes do not collect PQ measures such as phase angle or reactive power.

The main challenge is to go beyond manual methods based on the intuition and heuristics of human experts...it is crucial to develop the machine intelligence needed to automate and scale up the analytics on billions of PMU measurements and terabytes of data on a daily basis and in real time. \cite{mohsenian-rad_distribution_2018}

